### 2018-11-22 Sections/physical_architectures_for_quantum_computing.tex
Finished QND

In Sec.~\ref{sec:KLM_univ} we showed that with strong non-linearities\index{Non-linearities} at our disposal, scalable photonic quantum computing is possible. However, the interaction strengths of such devices available in the lab today are minuscule compared to the full $\pi$ phase-shift required for NS and CNOT gate constructions. In LOQC this problem is circumvented using measurement-induced non-linearities, which while are sufficiently strong, are also necessarily non-deterministic, mandating substantial error correction resource overheads to accommodate gate failure.

More recently, as an alternative to using post-selection to simulate strong optical non-linearities, it was shown that by introducing strong coherent states, the strength of the non-linear interaction can be effectively amplified arbitrarily, allowing even very weak non-linearities to be employed for deterministic entangling gate operations \cite{bib:Munro05}, compensated for using strong coherent states. Thankfully, strong coherent states are an easy resource to come by nowadays.

@@

The key ingredient here is the cross-Kerr interaction, which obeys the Hamiltonian,
\begin{align}
\hat{H}_\mathrm{ck} = \hbar \chi \hat{n}_a \hat{n}_b,	
\end{align}
where \mbox{$\hat{n}_a = \hat{a}^\dag \hat{a}$} and \mbox{$\hat{n}_b = \hat{b}^\dag \hat{b}$} are the photon-number operators for modes $a$ and $b$ respectively, and $\chi$ is the interaction strength, which is typically very small in the lab. This Hamiltonian generates the unitary transformation,
\begin{align}
\hat{U}_\mathrm{ck} = e^{i\theta\hat{n}_a\hat{n}_b}.
\end{align}
The magnitude of the induced phase-shift is now proportional to photon-number and,  
\begin{align}
\theta = \chi t,	
\end{align}
where $t$ is the interaction time. For strongly entangling gates we need \mbox{$\theta \approx \pi$}.

Applying this operation between a coherent state and a photon-number state implements the transformation, 
\begin{align}
\hat{U}_\mathrm{ck} \ket\alpha \ket{n} = \ket{\alpha e^{i\theta n}} \ket{n}.	
\end{align}
Note that the phase-shift accumulated by the coherent state is proportional to the photon-number in the other mode, thereby entangling the two modes via their shared dependence on $n$.

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{weak_ck_parity_gate}
\caption{Construction of a 2-mode, polarisation-encoded, photonic parity gate using an ancillary qubus coherent state $\ket\alpha$, mediating entangling photonic interactions between $\ket{\psi_a}$ and $\ket{\psi_b}$ via weak cross-Kerr non-linearities (denoted by the controlled-$\theta$ gates). The polarising beamsplitters\index{Polarising beamsplitters} are used to switch between polarisation and dual-rail encoding. The qubus is an optical channel, potentially across long distances over the quantum internet for performing distributed gates. The measurement $M$ is a homodyne measurement\index{Homodyne measurements}, which feedforwards an $X$-quadrature measurement outcome to a local phase correction. This gate could be used for preparing distributed photonic cluster states, a resource for universal quantum computation.}\label{fig:weak_ck_parity}	
\end{figure*}

Consider the parity measurement circuit shown in Fig.~\ref{fig:weak_ck_parity}. Let us begin with two polarisation-encoded photonic qubits, which might be separated over long distances, and a coherent state in the qubus mode,
\begin{align}
\ket{\psi_\mathrm{in}} &= (\alpha_{HH} \ket{H}\ket{H} + \alpha_{HV} \ket{H}\ket{V} \nonumber\\
&+\alpha_{VH} \ket{V}\ket{H} + \alpha_{VV} \ket{V}\ket{V})\ket\alpha.
\end{align}
Applying the cross-Kerr interactions leaves us in the state,
\begin{align}
\hat{U}_\mathrm{gate} \ket{\psi_\mathrm{in}}\ket\alpha &= [\alpha_{HH} \ket{H}\ket{H}] + \alpha_{VV} \ket{V}\ket{V}]\ket\alpha \nonumber\\
	&+ \alpha_{HV} \ket{H}\ket{V}\ket{\alpha e^{i\theta}}\nonumber\\
	&+ \alpha_{VH} \ket{V}\ket{H}\ket{\alpha e^{-i\theta}}.
\end{align}
Now the qubus state is in some superposition of $\ket\alpha$, $\ket{\alpha e^{i\theta}}$ and $\ket{\alpha e^{-i\theta}}$. The key observation is that these three coherent basis states become highly distinguishable for large $|\alpha|$. Specifically, a homodyne measurement on the qubus that projects onto \mbox{$x=0$}, approximately leaves us in the state,
\begin{align}
	\ket{\psi_\mathrm{out}} = \alpha_{HH}\ket{H}\ket{H} + \alpha_{VV}\ket{V}\ket{V},
\end{align}
which corresponds to a maximally-entangling parity or Bell projection\index{Bell!Measurement}.

@@

This type of non-local gate lends itself very naturally to distributed, network-based implementation, where the quantum internet is employed to mediate the qubus, potentially over long distances. Note that unlike LOQC fusion gates, this gate is non-destructive, and does not require measuring any photonic qubits, only the qubus.

The downside of this protocol, and other qubus-based protocols based on the same idea, is its sensitivity to loss. This is because the qubus is effectively in a cat state (Sec.~\ref{sec:cat_enc}), whose sensitivity to decoherence increases rapidly with the coherent amplitude $|\alpha|$. This will effectively place hard limits on how remote Alice and Bob can be in a distributed setting, depending on the loss characteristics of the quantum channel shared between them. It also presents the engineer with a direct tradeoff between decoherence of the qubus and distinguishability of the qubus basis states, both of which increase with $|\alpha|$.

>>>>

In Sec.~\ref{sec:KLM_univ} we showed that with strong non-linearities\index{Non-linearities} at our disposal, scalable photonic quantum computing is possible. However, the interaction strengths of such materials available in the lab today are minuscule compared to the full $\pi$ phase-shift required for NS and CNOT gate constructions. In LOQC this problem is circumvented using measurement-induced non-linearities, which while being sufficiently strong, are also necessarily non-deterministic, mandating substantial error correction resource overheads to accommodate gate failure.

More recently, as an alternative to using post-selection to simulate strong optical non-linearities, it was shown that by introducing strong coherent states, the strength of the non-linear interaction can be effectively amplified arbitrarily, allowing even very weak non-linearities to be employed for deterministic entangling gate operations \cite{bib:Munro05}, compensated for using strong coherent states. Thankfully, strong coherent states are an easy resource to come by nowadays!

@@

The key ingredient here is the cross-Kerr interaction, which obeys the Hamiltonian,
\begin{align}
\hat{H}_\mathrm{ck} = \hbar \chi \hat{n}_a \hat{n}_b,	
\end{align}
where \mbox{$\hat{n}_a = \hat{a}^\dag \hat{a}$} and \mbox{$\hat{n}_b = \hat{b}^\dag \hat{b}$} are the photon-number operators\index{Photon-number operators} for modes $a$ and $b$ respectively, and $\chi$ is the interaction strength\index{Interaction strength}, which is typically very small in the lab. This Hamiltonian generates the unitary transformation,
\begin{align}
\hat{U}_\mathrm{ck} = e^{i\theta\hat{n}_a\hat{n}_b}.
\end{align}
The magnitude of the induced phase-shift is now proportional to photon-number and,  
\begin{align}
\theta = \chi t,	
\end{align}
where $t$ is the interaction time\index{Interaction time}. For strongly entangling gates we need \mbox{$\theta \approx \pi$}.

Applying this operation between a coherent state and a photon-number state implements the two-mode transformation, 
\begin{align}
\hat{U}_\mathrm{ck} \ket\alpha \ket{n} = \ket{\alpha e^{i\theta n}} \ket{n}.	
\end{align}
Note that the phase-shift accumulated by the coherent state is proportional to the photon-number in the other mode, thereby entangling the two modes via their shared dependence on $n$.

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{weak_ck_parity_gate}
\caption{Construction of a two-mode, polarisation-encoded, photonic parity gate using an ancillary qubus coherent state $\ket\alpha$, mediating entangling photonic interactions between $\ket{\psi_a}$ and $\ket{\psi_b}$ via weak cross-Kerr non-linearities (denoted by the controlled-$\theta$ gates). The polarising beamsplitters\index{Polarising beamsplitters} are used to switch between polarisation and dual-rail encoding. The qubus is an optical channel, potentially across long distances over the quantum internet for performing distributed gates. The measurement $M$ is a homodyne measurement\index{Homodyne measurements}, which feedforwards an $X$-quadrature measurement outcome to a local phase correction. This gate could be used for preparing distributed photonic cluster states, a resource for universal quantum computation.}\label{fig:weak_ck_parity}	
\end{figure*}

Consider the parity measurement circuit shown in Fig.~\ref{fig:weak_ck_parity}. Let us begin with two polarisation-encoded photonic qubits, which might be separated over long distances, and a coherent state in the shared qubus mode,
\begin{align}
\ket{\psi_\mathrm{in}} &= (\alpha_{HH} \ket{H}\ket{H} + \alpha_{HV} \ket{H}\ket{V} \nonumber\\
&+\alpha_{VH} \ket{V}\ket{H} + \alpha_{VV} \ket{V}\ket{V})\ket\alpha.
\end{align}
Applying the cross-Kerr interactions leaves us in the state,
\begin{align}
\hat{U}_\mathrm{gate} \ket{\psi_\mathrm{in}} &= [\alpha_{HH} \ket{H}\ket{H}] + \alpha_{VV} \ket{V}\ket{V}]\ket\alpha \nonumber\\
	&+ \alpha_{HV} \ket{H}\ket{V}\ket{\alpha e^{i\theta}}\nonumber\\
	&+ \alpha_{VH} \ket{V}\ket{H}\ket{\alpha e^{-i\theta}}.
\end{align}
Now the qubus state is in some superposition of $\ket\alpha$, $\ket{\alpha e^{i\theta}}$ and $\ket{\alpha e^{-i\theta}}$. The key observation is that these three coherent basis states become highly distinguishable for large $|\alpha|$. Specifically, a homodyne measurement on the qubus that projects onto \mbox{$x=0$}, approximately leaves us in the state,
\begin{align}
	\ket{\psi_\mathrm{out}} = \alpha_{HH}\ket{H}\ket{H} + \alpha_{VV}\ket{V}\ket{V},
\end{align}
which corresponds to a maximally-entangling parity or Bell projection\index{Bell!Measurement}.

@@

This type of non-local gate lends itself very naturally to distributed, network-based implementation, where the quantum internet is employed to mediate the qubus, potentially over long distances. Note that unlike polarising beamsplitter-based fusion gates, this gate is non-destructive, and does not require measuring any photonic qubits, only the qubus.

The downside of this protocol, and other qubus-based protocols based on the same idea, is its sensitivity to loss. This is because the qubus is effectively in a cat state (Sec.~\ref{sec:cat_enc}), whose sensitivity to decoherence increases rapidly with the coherent amplitude $|\alpha|$. This will effectively place hard limits on how remote Alice and Bob can be in a distributed setting, depending on the loss characteristics of the quantum channel shared between them. It also presents the engineer with a direct tradeoff between decoherence of the qubus (undesirable) and distinguishability of the qubus basis states (desirable), both of which increase with $|\alpha|$.

### 2018-11-22 Sections/protocols_for_the_quantum_internet.tex
Finished QND

\comment{To do! List abbrev.}

>>>>

When it comes to optical systems, measurement is typically \textit{destructive}\index{Destructive measurements}, i.e the photon (or other optical state) is destroyed in the process of measurement. An APD, for example, converts a photon to an electrical current and then the photon is gone. Can we measure the logical value of optical states without destroying them?

The answer is yes, via \textit{quantum non-demolition measurements} (QND). The central idea here is to entangle a system which mustn't be destroyed with an ancillary system that we can happily afford to lose. Because the two systems are correlated, a destructive measurement on the ancillary state yields an effective measurement on the primary system, but without destroying it.

The simplest example to illustrate this is by considering the measurement of a single qubit,
\begin{align}
\ket\psi = \alpha\ket{0} + \beta\ket{1}.	
\end{align}
We begin by introducing an additional ancillary qubit in the logical $\ket{0}$ state, which we maximally entangle to the primary system with a CNOT gate. This yields two redundantly encoded qubits,
\begin{align}
\hat{\mathrm{CNOT}}\ket\psi \ket{0} = \alpha\ket{0}\ket{0} + \beta\ket{1}\ket{1},
\end{align}
characterised by the same amplitudes as the original qubit. The ancilla is then measured (destructively), which reads out the original state of the primary system to which it was correlated, but which has not been destroyed and may freely continue on its journey.

Unfortunately, the required CNOT gate is cumbersome in optical architectures. But it can be done, and in Sec.~\ref{sec:KLM_univ} we describe in detail how such gates can be constructed.

The quantum circuit implementation for QND is shown in Fig.~\ref{fig:QND_circ}.

\begin{figure}[!htbp]
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\ket\psi} & \ctrl{1} & \qw & \hat{M}\ket\psi \\
    \lstick{\ket{0}} & \targ & \qw & \meter \\
} \nonumber
\end{align}
\captionspacefig \caption{Quantum non-demolition measurement of a single qubit. $\hat{M}$ is the measurement operator applied during measurement to the ancillary state, which may be destructive. The primary qubit has now been projected onto the measurement outcome $\hat{M}$, but has not been destroyed.}\index{Quantum non-demolition measurement (QND).}\label{fig:QND_circ}
\end{figure}
